\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=1.06cm,top=0.49cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}

\begin{center}
    \textbf{\Large Yishan CHEN}
\end{center}

\vspace{-15pt}
\begin{center}
    (+86) 150 0093 8707 \textbullet\
    WeChat: kristyn5942 \textbullet\
    \href{mailto:Kristyn921207@gmail.com}{Kristyn921207@gmail.com} \textbullet\
    \href{https://kristynchen.github.io/Persional-Website/}{Portfolio}
\end{center}

%====================
\vspace{-10pt}
\begin{center}
    \textbf{Education} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{Shanghai Jiao Tong University} | B.S. Electrical and Computer Engineering | Shanghai, China 
\hfill Expected Aug 2026  

Relevant Coursework: STAT4060J Computational Methods, STAT4710J Data Science and Analytics using Python \\
Scholarships: Taiwan Student Scholarship (2023--2025); Bai Xian Asia Future Leaders Scholarship (2024--2026)

\vspace{2pt}
\textbf{Keio University} | Exchange Program, Computer Science | Tokyo, Japan 
\hfill Mar 2025 -- Aug 2025  

\vspace{2pt}
\textbf{Université de Technologie de Troyes} | Exchange Program, French | Troyes, France 
\hfill Jan 2025 -- Feb 2025  

\vspace{2pt}
\textbf{Kwansei Gakuin University} | Exchange Program, Law | Hyogo, Japan 
\hfill Jan 2024 -- Feb 2024

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Projects} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{terny.ai -- Agentic AI Research Opportunity Matching System} \hfill Nov 2025 -- Present  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Developed a data aggregation system via web scrapers and LLMs to automate parsing and extraction from complex lab websites.
    \item Led the \textbf{Agentic AI Architecture} design, building a Multi-Agent coordination pipeline for research topic comprehension, student profile modeling, and bidirectional matching.
    \item Orchestrated cross-source API calls and workflows using Codex and Antigravity, integrating event logging and stack tracing, with Git/GitHub for version control.
\end{itemize}

\vspace{2pt}
\textbf{GNN \& Transformer Material Property Prediction Engine} \hfill Dec 2025 -- Present  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Engineered an automated data pipeline for cleaning, aggregating, and multi-dimensional node vector mapping of materials science datasets (OC22/DFT).
    \item Independently built a computational backbone integrating Graph Neural Networks (GNNs) and Transformers, heavily refactoring core PyTorch clusters for cross-model reusability.
\end{itemize}

\vspace{2pt}
\textbf{Scaled Data Regression Engine: Structured House Price Prediction} \hfill Sep 2025 -- Dec 2025  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Processed a 250k+ dataset with 60+ features using NumPy and pandas to abstract and aggregate engineering data.
    \item Built a linear regression model via Hinge Gradient Descent in scikit-learn, optimizing performance via hyperparameter tuning.
    \item Delivered a highly reusable validation module, achieving high-precision predictions with an RMSE of 0.38.
\end{itemize}

\vspace{2pt}
\textbf{Fake News Text Classification Network \& Visualization Dashboard} \hfill Sep 2025 -- Dec 2025  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Cleaned and processed 70k news records using Python, applying text preprocessing techniques to optimize data quality.
    \item Extracted features via TF-IDF and trained classification models using SVM and gradient descent for dataset evaluation.
    \item Achieved 93\% accuracy through advanced text preprocessing and feature selection, outperforming baseline models.
    \item Developed an interactive Shiny dashboard to monitor end-user data predictions, encapsulating complex algorithmic outputs.
\end{itemize}

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Leadership \& Activities} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{Youth Volunteer Association} \hfill China  
Vice Head, Publicity Department \hfill Sep 2022 -- Aug 2024  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Led external communications for charity/educational programs, coordinating social media content and campus promotion.
    \item Led a 30-member team on a two-week teaching support program in Eryuan (Yunnan), overseeing planning, coordination, and impact dissemination.
\end{itemize}

\vspace{2pt}
\textbf{Student Association} \hfill Shanghai, China  
Honorary Member, Publicity Department \hfill Sep 2022 -- Aug 2024  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Supported college-wide event planning and execution, regularly designing merchandise and managing online sales.
\end{itemize}

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Skills} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-3pt}

\textbf{AI Applications \& Engineering:} Agentic Workflow, LLM Prompt Engineering, Codex Code Gen \\
\textbf{Data \& Algorithms:} Python, PyTorch (GNN/Transformer), pandas, NumPy, scikit-learn, SQL \\
\textbf{Development \& Tools:} Git, Shiny, MATLAB, C/C++ \\
\textbf{Languages:} Chinese (Native), English (Fluent), Japanese (Conversational)

\end{document}
