\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=1.06cm,top=0.49cm,right=1.06cm,bottom=0.49cm]{geometry}
\linespread{1}

\begin{document}

\begin{center}
    \textbf{\Large Yishan CHEN}
\end{center}

\vspace{-15pt}
\begin{center}
    (+86) 150 0093 8707 \textbullet\
    WeChat: kristyn5942 \textbullet\
    \href{mailto:Kristyn921207@gmail.com}{Kristyn921207@gmail.com} \textbullet\
    \href{https://kristynchen.github.io/Personal-Website/}{Portfolio}
\end{center}

%====================
\vspace{-10pt}
\begin{center}
    \textbf{Education} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{Shanghai JiaoTong University} | B.S. Electrical and Computer Engineering | Shanghai, China 
\hfill Aug 2026  

Relevant Coursework: STAT4060J Computational Methods, STAT4710J Data Science and Analytics using Python \\
Scholarships: Taiwan Student Scholarship (2023--2025); Bai Xian Asia Future Leaders Scholarship (2024--2026)

\vspace{2pt}
\textbf{Keio University} | Exchange Program, Computer Science | Tokyo, Japan 
\hfill Mar 2025 -- Aug 2025  

\vspace{2pt}
\textbf{Université de Technologie de Troyes} | Exchange Program, French | Troyes, France 
\hfill Jan 2025 -- Feb 2025  

\vspace{2pt}
\textbf{Kwansei Gakuin University} | Exchange Program, Law | Hyogo, Japan 
\hfill Jan 2024 -- Feb 2024

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Projects} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{\href{https://terny.ai/}{terny.ai} -- Agentic AI Research Opportunity Matching System} \hfill Nov 2025 -- Present  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Developed a data aggregation system via scrapers and LLMs to extract lab information and match student abilities to research opportunities.
    \item Led the \textbf{Agentic AI Architecture} design, building a Multi-Agent coordination pipeline for topic comprehension.
    \item Orchestrated workflows using Codex and Antigravity, integrating event logging and Git/GitHub version control.
\end{itemize}

\vspace{2pt}
\textbf{GNN \& Transformer Material Property Prediction Engine} \hfill Dec 2025 -- Present  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Engineered an automated data pipeline for comprehensive cleaning, aggregating, and multi-dimensional node vector mapping of OC22/DFT datasets.
    \item Built a computational backbone integrating Graph Neural Networks and Transformers. Refactored a reusable PyTorch training backbone for scalable cross-model experimentation.
\end{itemize}

\vspace{2pt}
\textbf{Scaled Data Regression Engine: Structured House Price Prediction} \hfill Sep 2025 -- Dec 2025  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Processed a 250k+ dataset with 60+ features using NumPy and pandas to engineered feature abstractions for predictive modeling.
    \item Built a linear regression model via Hinge Gradient Descent in sklearn, optimizing performance through targeted hyperparameter tuning.
    \item Delivered a highly reusable validation module, achieving high-precision predictions with RMSE of 0.38.
\end{itemize}

\vspace{2pt}
\textbf{Fake News Text Classification Network \& Visualization Dashboard} \hfill Sep 2025 -- Dec 2025  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Cleaned and processed 70k+ news records using Python with advanced text preprocessing to improve data quality and feature robustness.
    \item Extracted TF-IDF feature vectors and trained SVM classifiers via gradient descent, achieving 93\% accuracy and outperforming baseline models.
    \item Built an interactive Shiny dashboard to visualize real-time predictions, translating complex model outputs into an accessible user interface.
\end{itemize}

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Leadership \& Activities} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-5pt}

\textbf{Youth Volunteer Association} 
Vice Head, Publicity Department \hfill Sep 2022 -- Aug 2024  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Led external communications for charity programs, heavily coordinating social media content and campus promotion to drive student engagement.
    \item Led a 30-member team on a two-week teaching support program in Eryuan, directly overseeing planning, resource coordination, and impact dissemination.
\end{itemize}

\vspace{2pt}
\textbf{Student Association}
Honorary Member, Publicity Department \hfill Sep 2022 -- Aug 2024  
\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=15pt]
    \item Supported college-wide event planning and execution, frequently designing custom merchandise and efficiently managing comprehensive online sales.
\end{itemize}

%====================
\vspace{-5pt}
\begin{center}
    \textbf{Skills} \\
    \vspace{-5pt}
    \hrulefill
\end{center}
\vspace{-3pt}

\textbf{AI Applications \& Engineering:} Agentic Workflow, LLM Prompt Engineering, AI-assisted Code Gen (Codex, Antigravity) \\
\textbf{Data \& Algorithms:} Python, PyTorch (GNN/Transformer), pandas, NumPy, SQL, R \\
\textbf{Development \& Tools:} Git, Shiny (Frontend UI Dashboard), MATLAB, C/C++ \\
\textbf{Languages:} Chinese (Native), English (Fluent), Japanese (Conversational)

\end{document}
